Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
caption for EBV residuals figure

\begin{figure}
\begin{center}
\epsfig{file=ebv_2comp.eps, width=2.5in, angle=90}
\caption{\label{fig:resid} Residuals for best-fit $E(B-V)_{2comp}$ as a 
function of SFD $E(B-V)$.}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\epsfig{file=ebv_2comp.eps, width=2.5in, angle=90}
\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$. The grayscale represents the conditional probability within each
bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
and lower black lines represent the moving 75th and 25th percentiles 
respectively.}
\end{center}
\end{figure}
